### 2025-04-25 data-visualization.qmd
20250408 - plotly
20250425 - scatterplot with rug plot/marginal densigram

```{r}
library("nflplotR")
library("plotly")
library("gghighlight")
library("ggridges")
library("ggExtra")
library("tidyverse")
```

@@

@@

@@

We can also add a marginal density/histogram, as in @fig-scatterplot12 using the `ggExtra` package [@R-ggExtra]:

```{r}
#| label: fig-scatterplot12
#| fig-cap: "Scatterplot With Marginal Density/Histogram."
#| fig-alt: "Scatterplot With Marginal Density/Histogram."

@@

>>>>

```{r}
library("nflplotR")
library("plotly")
library("gghighlight")
library("ggridges")
library("ggExtra")
library("patchwork")
library("tidyverse")
```

@@

plotly::ggplotly(plot_ypcByPlayerAge)
```

@@

### Scatterplot with Rug Plot {#sec-scatterplotRugPlot}

We can also add a rug plot, as in @fig-scatterplot12.

```{r}
#| label: fig-scatterplot12
#| fig-cap: "Scatterplot With Rug Plot."
#| fig-alt: "Scatterplot With Rug Plot."

ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age,
    y = rushing_yards)) +
  geom_point() +
  geom_smooth() +
  geom_rug(
    col = "#800000",
    alpha = 0.2) +
  coord_cartesian(
    xlim = c(20,40),
    ylim = c(0,NA)) +
  scale_x_continuous(
    breaks = seq(from = 20, to = 40, by = 5)
  ) +
  scale_y_continuous(
    breaks = seq(from = 0, to = 2500, by = 250)
  ) +
  labs(
    x = "Running Back's Age (years)",
    y = "Rushing Yards (Season)",
    title = "NFL Rushing Yards (Season) by Player Age",
    subtitle = "(Among Running Backs)"
  ) +
  theme_classic()
```

@@

We can also add a marginal density/histogram, as in @fig-scatterplot13 using the `ggExtra` package [@R-ggExtra]:

```{r}
#| label: fig-scatterplot13
#| fig-cap: "Scatterplot With Marginal Density/Histogram."
#| fig-alt: "Scatterplot With Marginal Density/Histogram."

@@

Or we can create the plots manually, as in @fig-scatterplot14 using the `patchwork` package [@R-patchwork]:

```{r}
#| label: fig-scatterplot14
#| fig-cap: "Scatterplot With Marginal Density/Histogram."
#| fig-alt: "Scatterplot With Marginal Density/Histogram."

dens1 <- ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = age)) +
  coord_cartesian(
    xlim = c(20,40),
    expand = FALSE) +
  geom_histogram(
    aes(y = after_stat(density)),
    color = "#000000",
    fill = "#0099F8"
  ) +
  geom_density(
    color = "#000000",
    fill = "#F85700",
    alpha = 0.6 # add transparency
  ) +
  theme_void()

dens2 <- ggplot2::ggplot(
  data = rb_seasonal,
  aes(
    x = rushing_yards)) +
  geom_histogram(
    aes(y = after_stat(density)),
    color = "#000000",
    fill = "#0099F8"
  ) +
  geom_density(
    color = "#000000",
    fill = "#F85700",
    alpha = 0.6 # add transparency
  ) +
  theme_void() +
  coord_flip(
    ylim = c(0, NA),
    expand = FALSE)

dens1 + patchwork::plot_spacer() + plot_ypcByPlayerAge + dens2 + 
  patchwork::plot_layout(
    ncol = 2, 
    nrow = 2, 
    widths = c(4, 1),
    heights = c(1, 4)
  )
```
